%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    [Closed the gap between AI power users and everyday engineers across a 300-person web engineering org and the company as a whole by focusing on simple, broadly accessible unlocks.] % Summary
    {AI Champion, Developer Experience} % Job title
    {Block (Square)} % Organization
    {Remote} % Location
    {Jan. 2025 - Feb. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Eliminated per-engineer AI setup costs by building reusable skills for common tools (Slack, Jira, code review) that shipped as defaults — no configuration required.}
        \item {Scaled agent configuration across 12,000+ internal repositories by leading a company-wide initiative to establish AI-ready defaults everywhere, not just for teams already bought in.}
        \item {Gave every web engineer a shared foundation by shipping standardized AI coding rules, automated PR review workflows, and a plugin distribution system.}
        \item {Accelerated adoption across the org by running demos and building documentation around what works day-to-day.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  [Built the infrastructure and ran the experiments that drove merchant signup conversion for a platform serving millions of users.]
    {Software Engineer, Frontend Infrastructure \& Growth} % Job title
    {Block (Square)} % Organization
    {Remote} % Location
    {Aug. 2022 - Feb. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Enabled 24M+ user experiments in production by designing server-side feature flag infrastructure for anonymous users from scratch.}
        \item {Removed a deployment bottleneck slowing the whole team by cutting pipeline times 87\% (30--40 min to \textasciitilde5 min) through parallelization and resource tuning.}
        \item {Fixed a silent performance regression degrading page speed across multiple teams by tracing an 11x spike in unused CSS to a dependency upgrade, bringing Lighthouse scores 58 $\rightarrow$ 72 and LCP 6.0s $\rightarrow$ 4.4s.}
        \item {Shipped measurable signup conversion improvements by owning A/B experiments end-to-end across two frontend codebases — flag configuration, exposure logging, data science coordination, and graduated rollout to 100\% of traffic.}
        \item {Made incidents diagnosable by integrating error tracking with feature flag context, giving on-call engineers immediate visibility into what code was active when something broke.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    [Owned full-stack delivery for client-facing features and internal security infrastructure across multiple teams.]
    {Software Engineer} % Job title
    {Cisco} % Organization
    {Hybrid} % Location
    {Sep. 2017 - Jul. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Reduced security risk for internal teams by building and owning a performant API serving company security objectives.}
        \item {Eliminated manual infrastructure risk by transitioning the product to deploy via infrastructure as code.}
        \item {Kept delivery speed high without sacrificing quality by leading architecture decisions across the team's mainline product.}
        \item {Cut new engineer ramp time by overhauling onboarding documentation and code review workflows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Security Research Engineer} % Job title
    {Cisco} % Organization
    {Knoxville, TN} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Strengthened product security by evaluating systems for vulnerabilities through network traffic analysis, source code review, and process inspection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Undergraduate Teaching Assistant} % Job title
  %   {University of Tennessee} % Organization
  %   {Knoxville, TN} % Location
  %   {Jan. 2016 - May. 2017} % Date(s)
  %   {
  %     \begin{cvitems}
  %       \item {Helped 300-level systems programming students build foundational skills by leading lab sessions and holding regular office hours.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}